Performances Code

### 2019-01-29 Scripts/performances.rmd
aggregating rfe plots from all balancing techniques

@@

```{r}
#rfeModel_all <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/all/RFE/rfeModel_all.rds")
rfeModel_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
#rfeModel_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OC/RFE/rfeModel_oc.rds")
#rfeModel_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OP/RFE/rfeModel_op.rds")

#resampdata <- rbind.data.frame(rfeModel_all$results,rfeModel_dist$results,rfeModel_oc$results,rfeModel_op$results)

#resampdata$`Predictor Type` <- c(rep("Combined", nrow(rfeModel_all$results)),
#                                 rep("Distance", nrow(rfeModel_dist$results)),
#                                 rep("OC", nrow(rfeModel_oc$results)),
#                                 rep("OP", nrow(rfeModel_op$results)))

#resampdata$`Predictor Type` <- factor(resampdata$`Predictor Type`)

resampdata_10kb <- rfeModel_dist$results[1:6,]

pt10kb <- ggplot(resampdata_10kb, aes(x=Variables, y=AUPRC)) +
  geom_point()+
  geom_line() +
  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), width=1)+
  scale_x_discrete(name="Number of Features", 
                   breaks=c("2", "4", "8", "16", "32", "64"), 
                   labels=c("2", "4", "8", "16", "32", "64"), 
                   limits=as.character(c(1:64)))+
  theme_minimal()+
  ylim(0,.5)

@@

```{r}
#rfeModel_all <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/all/RFE/rfeModel_all.rds")
rfeModel_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
#rfeModel_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OC/RFE/rfeModel_oc.rds")
#rfeModel_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OP/RFE/rfeModel_op.rds")

#resampdata <- rbind.data.frame(rfeModel_all$results,rfeModel_dist$results,rfeModel_oc$results,rfeModel_op$results)

#resampdata$`Predictor Type` <- c(rep("Combined", nrow(rfeModel_all$results)),
#                                 rep("Distance", nrow(rfeModel_dist$results)),
#                                 rep("OC", nrow(rfeModel_oc$results)),
#                                 rep("OP", nrow(rfeModel_op$results)))

#resampdata$`Predictor Type` <- factor(resampdata$`Predictor Type`)

resampdata_25kb <- rfeModel_dist$results[1:6,]

pt25kb <- ggplot(resampdata_25kb, aes(x=Variables, y=AUPRC)) +
  geom_point()+
  geom_line() +
  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), width=1)+
  scale_x_discrete(name="Number of Features", 
                   breaks=c("2", "4", "8", "16", "32", "64"), 
                   labels=c("2", "4", "8", "16", "32", "64"), 
                   limits=as.character(c(1:64)))+
  theme_minimal()+
  ylim(0,.5)

@@

```{r}
#rfeModel_all <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/all/RFE/rfeModel_all.rds")
rfeModel_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
#rfeModel_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OC/RFE/rfeModel_oc.rds")
#rfeModel_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OP/RFE/rfeModel_op.rds")

#resampdata <- rbind.data.frame(rfeModel_all$results,rfeModel_dist$results,rfeModel_oc$results,rfeModel_op$results)

#resampdata$`Predictor Type` <- c(rep("Combined", nrow(rfeModel_all$results)),
#                                 rep("Distance", nrow(rfeModel_dist$results)),
#                                 rep("OC", nrow(rfeModel_oc$results)),
#                                 rep("OP", nrow(rfeModel_op$results)))

#resampdata$`Predictor Type` <- factor(resampdata$`Predictor Type`)

resampdata_50kb <- rfeModel_dist$results[1:6,]

pt50kb <- ggplot(resampdata_50kb, aes(x=Variables, y=AUPRC)) +
  geom_point()+
  geom_line() +
  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), width=1)+
  scale_x_discrete(name="Number of Features", 
                   breaks=c("2", "4", "8", "16", "32", "64"), 
                   labels=c("2", "4", "8", "16", "32", "64"), 
                   limits=as.character(c(1:64)))+
  theme_minimal()+
  ylim(0,.5)

@@

```{r}
#rfeModel_all <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/all/RFE/rfeModel_all.rds")
rfeModel_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
#rfeModel_oc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OC/RFE/rfeModel_oc.rds")
#rfeModel_op <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/OP/RFE/rfeModel_op.rds")

#resampdata <- rbind.data.frame(rfeModel_all$results,rfeModel_dist$results,rfeModel_oc$results,rfeModel_op$results)

#resampdata$`Predictor Type` <- c(rep("Combined", nrow(rfeModel_all$results)),
#                                 rep("Distance", nrow(rfeModel_dist$results)),
#                                 rep("OC", nrow(rfeModel_oc$results)),
#                                 rep("OP", nrow(rfeModel_op$results)))

#resampdata$`Predictor Type` <- factor(resampdata$`Predictor Type`)

resampdata_100kb <- rfeModel_dist$results[1:6,]

pt100kb <- ggplot(resampdata_100kb, aes(x=Variables, y=AUPRC)) +
  geom_point()+
  geom_line() +
  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), width=1)+
  scale_x_discrete(name="Number of Features", 
                   breaks=c("2", "4", "8", "16", "32", "64"), 
                   labels=c("2", "4", "8", "16", "32", "64"), 
                   limits=as.character(c(1:64)))+
  theme_minimal()+
  ylim(0,.5)

```{r}
#rfeModel_all <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/all/RFE/rfeModel_all.rds")
rfeModel_dist <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
#rfeModel_oc <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OC/RFE/rfeModel_oc.rds")
#rfeModel_op <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/OP/RFE/rfeModel_op.rds")

#resampdata <- rbind.data.frame(rfeModel_all$results,rfeModel_dist$results,rfeModel_oc$results,rfeModel_op$results)

#resampdata$`Predictor Type` <- c(rep("Combined", nrow(rfeModel_all$results)),
#                                 rep("Distance", nrow(rfeModel_dist$results)),
#                                 rep("OC", nrow(rfeModel_oc$results)),
#                                 rep("OP", nrow(rfeModel_op$results)))

#resampdata$`Predictor Type` <- factor(resampdata$`Predictor Type`)

resampdata_10kb_k562 <- rfeModel_dist$results[1:6,]

pt10kb_k562 <- ggplot(resampdata_10kb_k562, aes(x=Variables, y=AUPRC)) +
  geom_point()+
  geom_line() +
  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), width=1)+
  scale_x_discrete(name="Number of Features", 
                   breaks=c("2", "4", "8", "16", "32", "64"), 
                   labels=c("2", "4", "8", "16", "32", "64"), 
                   limits=as.character(c(1:64)))+
  theme_minimal()+
  ylim(0,.5)

```{r}
#rfeModel_all <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/all/RFE/rfeModel_all.rds")
rfeModel_dist <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
#rfeModel_oc <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OC/RFE/rfeModel_oc.rds")
#rfeModel_op <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/OP/RFE/rfeModel_op.rds")

#resampdata <- rbind.data.frame(rfeModel_all$results,rfeModel_dist$results,rfeModel_oc$results,rfeModel_op$results)

>>>>

##Tables of AUPRC

@@

```{r}
rfeModel_None_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
rfeModel_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/RFE/rfeModel_dist.rds")
rfeModel_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/RFE/rfeModel_dist.rds")
rfeModel_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/RFE/rfeModel_dist.rds")
rfeModel_ROSE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROSE/Distance/RFE/rfeModel_dist.rds")

rfeModel_None_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
rfeModel_RUS_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/RUS/Distance/RFE/rfeModel_dist.rds")
rfeModel_ROS_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROS/Distance/RFE/rfeModel_dist.rds")
rfeModel_SMOTE_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/SMOTE/Distance/RFE/rfeModel_dist.rds")
rfeModel_ROSE_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/10kb/Ensemble/ROSE/Distance/RFE/rfeModel_dist.rds")

#None
resampdata_None_10kb <- rbind.data.frame(rfeModel_None_dist$results,rfeModel_None_dist_K562$results)
resampdata_None_10kb$CL <- c(rep("GM12878", dim(rfeModel_None_dist$results)[1]),
                             rep("K562", dim(rfeModel_None_dist_K562$results)[1]))

rfeplot_None_10kb <- ggplot(resampdata_None_10kb, aes(x=Variables, y=AUPRC, color=CL)) +
  geom_point(position = position_dodge(width = 3))+
  geom_line() +
  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
                width=5,
                position = position_dodge(width = 3))+
  scale_color_discrete(name="Cell Line")+
  scale_x_discrete(name="Number of Features", 
                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
                   limits=as.character(c(1:138)))+
  theme_minimal()#+
  #ylim(0,.5)

#RUS
resampdata_RUS_10kb <- rbind.data.frame(rfeModel_RUS_dist$results,rfeModel_RUS_dist_K562$results)
resampdata_RUS_10kb$CL <- c(rep("GM12878", dim(rfeModel_RUS_dist$results)[1]),
                             rep("K562", dim(rfeModel_RUS_dist_K562$results)[1]))

rfeplot_RUS_10kb <- ggplot(resampdata_RUS_10kb, aes(x=Variables, y=AUPRC, color=CL)) +
  geom_point(position = position_dodge(width = 3))+
  geom_line() +
  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
                width=5,
                position = position_dodge(width = 3))+
  scale_color_discrete(name="Cell Line")+
  scale_x_discrete(name="Number of Features", 
                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
                   limits=as.character(c(1:138)))+
  theme_minimal()#+
  #ylim(0,1)

#ROS
resampdata_ROS_10kb <- rbind.data.frame(rfeModel_ROS_dist$results,rfeModel_ROS_dist_K562$results)
resampdata_ROS_10kb$CL <- c(rep("GM12878", dim(rfeModel_ROS_dist$results)[1]),
                             rep("K562", dim(rfeModel_ROS_dist_K562$results)[1]))

rfeplot_ROS_10kb <- ggplot(resampdata_ROS_10kb, aes(x=Variables, y=AUPRC, color=CL)) +
  geom_point(position = position_dodge(width = 3))+
  geom_line() +
  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
                width=5,
                position = position_dodge(width = 3))+
  scale_color_discrete(name="Cell Line")+
  scale_x_discrete(name="Number of Features", 
                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
                   limits=as.character(c(1:138)))+
  theme_minimal()#+
  #ylim(0,1)

#SMOTE
resampdata_SMOTE_10kb <- rbind.data.frame(rfeModel_SMOTE_dist$results,rfeModel_SMOTE_dist_K562$results)
resampdata_SMOTE_10kb$CL <- c(rep("GM12878", dim(rfeModel_SMOTE_dist$results)[1]),
                             rep("K562", dim(rfeModel_SMOTE_dist_K562$results)[1]))

rfeplot_SMOTE_10kb <- ggplot(resampdata_SMOTE_10kb, aes(x=Variables, y=AUPRC, color=CL)) +
  geom_point(position = position_dodge(width = 3))+
  geom_line() +
  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
                width=5,
                position = position_dodge(width = 3))+
  scale_color_discrete(name="Cell Line")+
  scale_x_discrete(name="Number of Features", 
                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
                   limits=as.character(c(1:138)))+
  theme_minimal()#+
  #ylim(0,1)

#ROSE
resampdata_ROSE_10kb <- rbind.data.frame(rfeModel_ROSE_dist$results,rfeModel_ROSE_dist_K562$results)
resampdata_ROSE_10kb$CL <- c(rep("GM12878", dim(rfeModel_ROSE_dist$results)[1]),
                             rep("K562", dim(rfeModel_ROSE_dist_K562$results)[1]))

rfeplot_ROSE_10kb <- ggplot(resampdata_ROSE_10kb, aes(x=Variables, y=AUPRC, color=CL)) +
  geom_point(position = position_dodge(width = 3))+
  geom_line() +
  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
                width=5,
                position = position_dodge(width = 3))+
  scale_color_discrete(name="Cell Line")+
  scale_x_discrete(name="Number of Features", 
                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
                   limits=as.character(c(1:138)))+
  theme_minimal()#+
  #ylim(0,1)

#Combining 10 kb plots
ggarrange(rfeplot_None_10kb,
          rfeplot_RUS_10kb,
          rfeplot_ROS_10kb,
          rfeplot_SMOTE_10kb,
          rfeplot_ROSE_10kb,
          nrow = 3,
          ncol = 2,
          common.legend = TRUE,
          legend = "right")

@@

```{r}
rfeModel_None_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
rfeModel_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/RFE/rfeModel_dist.rds")
rfeModel_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/RFE/rfeModel_dist.rds")
rfeModel_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/RFE/rfeModel_dist.rds")
rfeModel_ROSE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROSE/Distance/RFE/rfeModel_dist.rds")

rfeModel_None_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
rfeModel_RUS_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/RUS/Distance/RFE/rfeModel_dist.rds")
rfeModel_ROS_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROS/Distance/RFE/rfeModel_dist.rds")
rfeModel_SMOTE_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/SMOTE/Distance/RFE/rfeModel_dist.rds")
rfeModel_ROSE_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/25kb/Ensemble/ROSE/Distance/RFE/rfeModel_dist.rds")

#None
resampdata_None_25kb <- rbind.data.frame(rfeModel_None_dist$results,rfeModel_None_dist_K562$results)
resampdata_None_25kb$CL <- c(rep("GM12878", dim(rfeModel_None_dist$results)[1]),
                             rep("K562", dim(rfeModel_None_dist_K562$results)[1]))

rfeplot_None_25kb <- ggplot(resampdata_None_25kb, aes(x=Variables, y=AUPRC, color=CL)) +
  geom_point(position = position_dodge(width = 3))+
  geom_line() +
  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
                width=5,
                position = position_dodge(width = 3))+
  scale_color_discrete(name="Cell Line")+
  scale_x_discrete(name="Number of Features", 
                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
                   limits=as.character(c(1:138)))+
  theme_minimal()#+
  #ylim(0,.5)

#RUS
resampdata_RUS_25kb <- rbind.data.frame(rfeModel_RUS_dist$results,rfeModel_RUS_dist_K562$results)
resampdata_RUS_25kb$CL <- c(rep("GM12878", dim(rfeModel_RUS_dist$results)[1]),
                             rep("K562", dim(rfeModel_RUS_dist_K562$results)[1]))

rfeplot_RUS_25kb <- ggplot(resampdata_RUS_25kb, aes(x=Variables, y=AUPRC, color=CL)) +
  geom_point(position = position_dodge(width = 3))+
  geom_line() +
  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
                width=5,
                position = position_dodge(width = 3))+
  scale_color_discrete(name="Cell Line")+
  scale_x_discrete(name="Number of Features", 
                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
                   limits=as.character(c(1:138)))+
  theme_minimal()#+
  #ylim(0,1)

#ROS
resampdata_ROS_25kb <- rbind.data.frame(rfeModel_ROS_dist$results,rfeModel_ROS_dist_K562$results)
resampdata_ROS_25kb$CL <- c(rep("GM12878", dim(rfeModel_ROS_dist$results)[1]),
                             rep("K562", dim(rfeModel_ROS_dist_K562$results)[1]))

rfeplot_ROS_25kb <- ggplot(resampdata_ROS_25kb, aes(x=Variables, y=AUPRC, color=CL)) +
  geom_point(position = position_dodge(width = 3))+
  geom_line() +
  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
                width=5,
                position = position_dodge(width = 3))+
  scale_color_discrete(name="Cell Line")+
  scale_x_discrete(name="Number of Features", 
                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
                   limits=as.character(c(1:138)))+
  theme_minimal()#+
  #ylim(0,1)

#SMOTE
resampdata_SMOTE_25kb <- rbind.data.frame(rfeModel_SMOTE_dist$results,rfeModel_SMOTE_dist_K562$results)
resampdata_SMOTE_25kb$CL <- c(rep("GM12878", dim(rfeModel_SMOTE_dist$results)[1]),
                             rep("K562", dim(rfeModel_SMOTE_dist_K562$results)[1]))

rfeplot_SMOTE_25kb <- ggplot(resampdata_SMOTE_25kb, aes(x=Variables, y=AUPRC, color=CL)) +
  geom_point(position = position_dodge(width = 3))+
  geom_line() +
  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
                width=5,
                position = position_dodge(width = 3))+
  scale_color_discrete(name="Cell Line")+
  scale_x_discrete(name="Number of Features", 
                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
                   limits=as.character(c(1:138)))+
  theme_minimal()#+
  #ylim(0,1)

#ROSE
resampdata_ROSE_25kb <- rbind.data.frame(rfeModel_ROSE_dist$results,rfeModel_ROSE_dist_K562$results)
resampdata_ROSE_25kb$CL <- c(rep("GM12878", dim(rfeModel_ROSE_dist$results)[1]),
                             rep("K562", dim(rfeModel_ROSE_dist_K562$results)[1]))

rfeplot_ROSE_25kb <- ggplot(resampdata_ROSE_25kb, aes(x=Variables, y=AUPRC, color=CL)) +
  geom_point(position = position_dodge(width = 3))+
  geom_line() +
  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
                width=5,
                position = position_dodge(width = 3))+
  scale_color_discrete(name="Cell Line")+
  scale_x_discrete(name="Number of Features", 
                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
                   limits=as.character(c(1:138)))+
  theme_minimal()#+
  #ylim(0,1)

@@

```{r}
rfeModel_None_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
rfeModel_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/RFE/rfeModel_dist.rds")
rfeModel_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/RFE/rfeModel_dist.rds")
rfeModel_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/RFE/rfeModel_dist.rds")
rfeModel_ROSE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROSE/Distance/RFE/rfeModel_dist.rds")

rfeModel_None_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
rfeModel_RUS_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/RUS/Distance/RFE/rfeModel_dist.rds")
rfeModel_ROS_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROS/Distance/RFE/rfeModel_dist.rds")
rfeModel_SMOTE_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/SMOTE/Distance/RFE/rfeModel_dist.rds")
rfeModel_ROSE_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/50kb/Ensemble/ROSE/Distance/RFE/rfeModel_dist.rds")

#None
resampdata_None_50kb <- rbind.data.frame(rfeModel_None_dist$results,rfeModel_None_dist_K562$results)
resampdata_None_50kb$CL <- c(rep("GM12878", dim(rfeModel_None_dist$results)[1]),
                             rep("K562", dim(rfeModel_None_dist_K562$results)[1]))

rfeplot_None_50kb <- ggplot(resampdata_None_50kb, aes(x=Variables, y=AUPRC, color=CL)) +
  geom_point(position = position_dodge(width = 3))+
  geom_line() +
  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
                width=5,
                position = position_dodge(width = 3))+
  scale_color_discrete(name="Cell Line")+
  scale_x_discrete(name="Number of Features", 
                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
                   limits=as.character(c(1:138)))+
  theme_minimal()#+
  #ylim(0,.5)

#RUS
resampdata_RUS_50kb <- rbind.data.frame(rfeModel_RUS_dist$results,rfeModel_RUS_dist_K562$results)
resampdata_RUS_50kb$CL <- c(rep("GM12878", dim(rfeModel_RUS_dist$results)[1]),
                             rep("K562", dim(rfeModel_RUS_dist_K562$results)[1]))

rfeplot_RUS_50kb <- ggplot(resampdata_RUS_50kb, aes(x=Variables, y=AUPRC, color=CL)) +
  geom_point(position = position_dodge(width = 3))+
  geom_line() +
  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
                width=5,
                position = position_dodge(width = 3))+
  scale_color_discrete(name="Cell Line")+
  scale_x_discrete(name="Number of Features", 
                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
                   limits=as.character(c(1:138)))+
  theme_minimal()#+
  #ylim(0,1)

#ROS
resampdata_ROS_50kb <- rbind.data.frame(rfeModel_ROS_dist$results,rfeModel_ROS_dist_K562$results)
resampdata_ROS_50kb$CL <- c(rep("GM12878", dim(rfeModel_ROS_dist$results)[1]),
                             rep("K562", dim(rfeModel_ROS_dist_K562$results)[1]))

rfeplot_ROS_50kb <- ggplot(resampdata_ROS_50kb, aes(x=Variables, y=AUPRC, color=CL)) +
  geom_point(position = position_dodge(width = 3))+
  geom_line() +
  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
                width=5,
                position = position_dodge(width = 3))+
  scale_color_discrete(name="Cell Line")+
  scale_x_discrete(name="Number of Features", 
                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
                   limits=as.character(c(1:138)))+
  theme_minimal()#+
  #ylim(0,1)

#SMOTE
resampdata_SMOTE_50kb <- rbind.data.frame(rfeModel_SMOTE_dist$results,rfeModel_SMOTE_dist_K562$results)
resampdata_SMOTE_50kb$CL <- c(rep("GM12878", dim(rfeModel_SMOTE_dist$results)[1]),
                             rep("K562", dim(rfeModel_SMOTE_dist_K562$results)[1]))

rfeplot_SMOTE_50kb <- ggplot(resampdata_SMOTE_50kb, aes(x=Variables, y=AUPRC, color=CL)) +
  geom_point(position = position_dodge(width = 3))+
  geom_line() +
  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
                width=5,
                position = position_dodge(width = 3))+
  scale_color_discrete(name="Cell Line")+
  scale_x_discrete(name="Number of Features", 
                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
                   limits=as.character(c(1:138)))+
  theme_minimal()#+
  #ylim(0,1)

#ROSE
resampdata_ROSE_50kb <- rbind.data.frame(rfeModel_ROSE_dist$results,rfeModel_ROSE_dist_K562$results)
resampdata_ROSE_50kb$CL <- c(rep("GM12878", dim(rfeModel_ROSE_dist$results)[1]),
                             rep("K562", dim(rfeModel_ROSE_dist_K562$results)[1]))

rfeplot_ROSE_50kb <- ggplot(resampdata_ROSE_50kb, aes(x=Variables, y=AUPRC, color=CL)) +
  geom_point(position = position_dodge(width = 3))+
  geom_line() +
  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
                width=5,
                position = position_dodge(width = 3))+
  scale_color_discrete(name="Cell Line")+
  scale_x_discrete(name="Number of Features", 
                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
                   limits=as.character(c(1:138)))+
  theme_minimal()#+
  #ylim(0,1)

@@

```{r}
rfeModel_None_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
rfeModel_RUS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/RUS/Distance/RFE/rfeModel_dist.rds")
rfeModel_ROS_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROS/Distance/RFE/rfeModel_dist.rds")
rfeModel_SMOTE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/SMOTE/Distance/RFE/rfeModel_dist.rds")
rfeModel_ROSE_dist <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/ROSE/Distance/RFE/rfeModel_dist.rds")

rfeModel_None_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/None/Distance/RFE/rfeModel_dist.rds")
rfeModel_RUS_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/RUS/Distance/RFE/rfeModel_dist.rds")
rfeModel_ROS_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROS/Distance/RFE/rfeModel_dist.rds")
rfeModel_SMOTE_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/SMOTE/Distance/RFE/rfeModel_dist.rds")
rfeModel_ROSE_dist_K562 <- readRDS("Z:/TAD_data_analysis/K562/100kb/Ensemble/ROSE/Distance/RFE/rfeModel_dist.rds")

#None
resampdata_None_100kb <- rbind.data.frame(rfeModel_None_dist$results,rfeModel_None_dist_K562$results)
resampdata_None_100kb$CL <- c(rep("GM12878", dim(rfeModel_None_dist$results)[1]),
                             rep("K562", dim(rfeModel_None_dist_K562$results)[1]))

rfeplot_None_100kb <- ggplot(resampdata_None_100kb, aes(x=Variables, y=AUPRC, color=CL)) +
  geom_point(position = position_dodge(width = 3))+
  geom_line() +
  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
                width=5,
                position = position_dodge(width = 3))+
  scale_color_discrete(name="Cell Line")+
  scale_x_discrete(name="Number of Features", 
                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
                   limits=as.character(c(1:138)))+
  theme_minimal()#+
  #ylim(0,.5)

#RUS
resampdata_RUS_100kb <- rbind.data.frame(rfeModel_RUS_dist$results,rfeModel_RUS_dist_K562$results)
resampdata_RUS_100kb$CL <- c(rep("GM12878", dim(rfeModel_RUS_dist$results)[1]),
                             rep("K562", dim(rfeModel_RUS_dist_K562$results)[1]))

rfeplot_RUS_100kb <- ggplot(resampdata_RUS_100kb, aes(x=Variables, y=AUPRC, color=CL)) +
  geom_point(position = position_dodge(width = 3))+
  geom_line() +
  geom_errorbar(aes(ymin=AUPRC-AUPRCSD, ymax=AUPRC+AUPRCSD), 
                width=5,
                position = position_dodge(width = 3))+
  scale_color_discrete(name="Cell Line")+
  scale_x_discrete(name="Number of Features", 
                   breaks=c("2", "4", "8", "16", "32", "64", "128"), 
                   labels=c("2", "4", "8", "16", "32", "64", "128"), 
                   limits=as.character(c(1:138)))+
  theme_minimal()#+
  #ylim(0,1)

#ROS
resampdata_ROS_100kb <- rbind.data.frame(rfeModel_ROS_dist$results,rfeModel_ROS_dist_K562$results)
resampdata_ROS_100kb$CL <- c(rep("GM12878", dim(rfeModel_ROS_dist$results)[1]),
                             rep("K562", dim(rfeModel_ROS_dist_K562$results)[1]))
